R for Clinical Study Reports and Submission

### 2021-10-10 project-management.Rmd

## Setting up for success

@@

### Work as a team

@@

### Design clean code architecture

@@

### Set capability boundaries

@@

### Contribute to the community

@@

For example, in the `esubdemo` project, we created the `pkgdown` website in https://elong0527.github.io/esubdemo/.

@@

For example, in `esubdemo` project, we setup [github actions](https://github.com/elong0527/esubdemo/actions)
for these work. It can be setup by using `usethis::use_github_action()` function.

>>>>

## Setting up for Success

@@

### Work as a Team

@@

### Design Clean Code Architecture

@@

### Set Capability Boundaries

@@

### Contribute to the Community

@@

For example, in the `esubdemo` project, we created the `pkgdown` website at <https://elong0527.github.io/esubdemo/>.

@@

For example, in `esubdemo` project, we setup [GitHub Actions](https://github.com/elong0527/esubdemo/actions)
for these work. It can be setup by using `usethis::use_github_action()` function.
